An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-10-12 aistats2017.tex
Whew, major update. Now to send email to John/Xinlei.

In the most similar prior works,~\citet{cutting_mh_2014} uses asymptotic
arguments based on the CLT to argue that its approximate acceptance test error
tends to zero as batch size increases, but no quantitative bounds are given.
In~\citet{icml2014c1_bardenet14}, explicit bounds are given, but they depend on
bounding:
\begin{equation}\label{eq:bad_bound}
    C_{\theta, \theta'} = \max_{1\leq i\leq N}|\log p(x_i\mid\theta') - \log p(x_i\mid\theta)|.
\end{equation}
Such bounds can be derived efficiently for models such as logistic regression,
but it is unclear how to derive them for a complex model such as a neural
network. In general, since a new $\theta'$ value is obtained each iteration, one
would need to iterate through all the $p(x_i\mid \theta')$ terms, defeating the
purpose of minibatch MCMC. In contrast, we use quantitative forms of the Central
Limit Theorem which rely on measurable statistics from a single minibatch. Thus
a sampler using our approach does not need to see data beyond the current
minibatch.

@@

\begin{proof}
The following bound is given immediately after Corollary 2 from~\citet{explicit-clt05}:
\begin{align*}
-6.4E|X|^3-2E|X| &\leq \sup_x|{\rm Pr}(t<x)-\Phi(x)|{\sqrt{n}} \\
&\leq 1.36E|X|^3.
\end{align*}
This bound applies to $x\geq 0$. Applying the bound to $-x$ when $x<0$
and combining with $x>0$, we obtain the weaker but unqualified bound
in Equation~(\ref{eq:clt-bounds}).
\end{proof}

@@

We start with a simple Gaussian mixture model, borrowing an experiment
from~\citet{langevin_2011}.  The parameter is 2-D, $\theta =
\langle \theta_1,\theta_2 \rangle$, and the parameter/data generation process is
%% \begin{equation}\label{eq:data_generation}
%%     (\theta_1,\theta_2) \sim \mathcal{N}((0,0), {\rm diag}(\sigma_1^2, \sigma_2^2));\quad \quad x_i \sim
%%     0.5 \cdot \mathcal{N}(\theta_1, \sigma_x^2) + 0.5 \cdot \mathcal{N}(\theta_1+\theta_2, \sigma_x^2).
%% \end{equation}
\begin{equation}\label{eq:data_generation}
\begin{split}
    \theta &\sim \mathcal{N}(0, {\rm diag}(\sigma_1^2,\sigma_2^2)) \\
    x_i & \sim 0.5 \cdot \mathcal{N}(\theta_1, \sigma_x^2) + 0.5 \cdot \mathcal{N}(\theta_1+\theta_2, \sigma_x^2).
\end{split}
\end{equation}
We set $\sigma_1^2 = 10, \sigma_2^2 = 1$ and $\sigma_x^2=2$.  We fix $\theta =
\langle 0,1 \rangle$. The original paper sampled 100 data points from this
distribution, and estimated the posterior in the parameters. We are interested
in performance on larger problems and so sampled 1,000,000 points to form the
posterior of $p(\theta)\prod_{i=1}^{1,000,000}p(x_i\mid \theta)$ with the same
prior from Equation~(\ref{eq:data_generation}). This produces a much sharper
posterior with two very narrow peaks.  Our goal is to reproduce the original
posterior, so we adjust the temperature to $T=10,000$.  Taking logs, we get the
target as shown in the far left of Figure~\ref{fig:gauss_mix_1}.

We run MCMC with our MH test and benchmark with~\citet{cutting_mh_2014}
and~\citet{icml2014c1_bardenet14}, all with initial minibatch size $m=100$.
For~\citet{cutting_mh_2014}, we increment minibatches by 100 and
for~\citet{icml2014c1_bardenet14}, we increase the minibatch size geometrically
with a ratio of $\gamma = 1.5$. These methods have different approaches to
repeated testing: the former uses an aggressive testing approach, explicitly
modeling correlation between tests and allowing many more tests for a given
$\delta$, while the latter uses discounting, allocating a fraction of the test
error $\delta$ to each minibatch test.

The tolerance for making a decision in~\citet{cutting_mh_2014} is
$\epsilon=0.005$, and the error bound control parameters
in~\citet{icml2014c1_bardenet14} are $p = 2$ and $\delta = 0.01$.  All methods
(including ours) use the same random walk proposer with covariance $\Sigma={\rm
diag}(0.15, 0.15)$.  Since the proposer generates a random walk, all shaping of
distribution of the samples is due to the MH test. All methods are run 5000
times to collect 5000 samples.

@@

We discretize the posterior coordinates into bins (non-overlapping ranges) with
respect to the two components of the parameter $\theta$.  The probability of a
sample falling into bin $i$ (denoted as $P_i$) is the integral of the true
posterior probability over the area of that bin.  A single sample from any of
the MH methods should therefore be multinomial with distribution $P$, and a set
of $n$ (ideally independent) samples should follow a ${\rm Multinomial}(P,n)$
distribution.  Since the ideal distribution is simple, we can use it to measure
the quality of the sample distributions rather than use general purpose tests
like KL-divergence or likelihood-ratio.  The latter are problematic with zero
counts in some bins as we have here.

In practice, it is difficult to compute multinomial probabilities for large $n$,
in that case the per-bin distributions are well-approximated by Poisson
distributions with parameter $\lambda_i=P_i n$. Given a set of samples
$\{\theta_1,\ldots,\theta_T\}$, let $c_j$ denote the number of individual samples
$\theta_i$ that fall in bin $j$ out of $N_{\rm bins}$ total. Then we have
\begin{equation}\label{eq:log_prob_poissons}
\begin{split}
    \log p(c_1, \ldots, c_{N_{\rm bins}} \mid P_1, \ldots, P_{N_{\rm bins}}) & =  \\
    \sum_{j=1}^{N_{\rm bins}} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)). & \\
\end{split}
\end{equation}
The results for each model are shown in Table~\ref{tab:poissons}.

While the Poisson results provide general guidance on the relative accuracy of
the models, it is difficult to interpret the scores, so we perform significance
tests to show the difference between the MCMC-sampled distributions and the
ground-truth.  We perform an approximate test using the Chi-Squared distribution
as the test statistic, which we also show in Table~\ref{tab:poissons}.

Both the Poisson values and the Chi-Squared test statistic result in similar
conclusions: our method is slightly superior to~\citet{cutting_mh_2014}, but
slightly worse than~\citet{icml2014c1_bardenet14}. We now show, however, that
minibatch size results suggest that our method dominates in terms of speed and
efficiency.

Figure~\ref{fig:gauss_mix_2} shows a histogram of the final minibatch sizes used
by the three methods in each iteration. Our method consumes significantly less
data; most minibatch sizes are smaller than 1000, and the average size is 210.
The other methods occasionally need to consume a large proportion of the
entire data set of one million elements; the average minibatch sizes are 15562
and 16857 for Korattikara 2014 and Bardenet 2014, respectively. The average
minibatch sizes accurately predict the running times of these methods since
all methods have a running time proportional to the total data consumed, with
one caveat: the method of~\citet{icml2014c1_bardenet14} requires a global bound
on the term $C_{\theta,\theta'}$ (see Equation~(\ref{eq:bad_bound})) over the
entire the data set at every iteration in order to calculate the error bound.
This bound must be either computed analytically using properties of the specific
dataset, or it must be checked at each sample if a black-box test is required.
We found that the sample code provided by the authors
of~\citet{icml2014c1_bardenet14} in fact computed this bound explicitly for each
sample generated, i.e. the implementation traversed the entire dataset for each
sample, providing no performance advantage over the complete test. For this
reason, we omitted the time to compute $C_{\theta,\theta'}$ from our
measurements of the running time of the sample implementation
of~\citet{icml2014c1_bardenet14}, and consider only the time to process the
minibatches.

%% In Figure ~\ref{fig:gauss_bardenet}, the value
%% of the first part and second part of equation (9)
%% in~\cite{icml2014c1_bardenet14} is shown with respect to the size of actual
%% minibatch data used. The second part which contains  the $C_{\theta,\theta'}$
%% term is larger than the first part, which means that the second part is
%% non-negligible and has to be calculated at every iteration. This is one of the
%% very time-consuming parts in this method.  {\color{blue} Daniel: I am not sure
%% if we should include this plot. Let me think about it and if we decide to
%% include it I will help rewrite the explanation.}

%% JFC - it would still be interesting to see this comparison, however:
%% (i) its important to include equation (9) and explain what the terms are.
%% (ii) the results dont look right. I wouldnt expect the first term to be
%% so small compared to the second and I'm fairly certain they should cross
%% in the illustrated range. It would be better to include both curves on
%% the same plot.

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.9\linewidth]{logistic_performance.png}
	\caption{
    Logistic regression performance (accuracy/log likelihood) based on
    cumulative data usage.
    }
	\label{fig:logistic_performance}
\end{figure*}
\begin{figure*}[t]
	\centering
	\includegraphics[width=0.9\linewidth]{minibatch_size_logistic.png}
	\caption{
    Counts of minibatch sizes in the MNIST logistic regression experiment
    (analogous to Figure~\ref{fig:gauss_mix_2}).
    }
	\label{fig:logistic_minibatch}
\end{figure*}

We next use logistic regression for the binary classification of 1s versus 7s in
the MNIST dataset~\citep{lecun-mnisthandwrittendigit-2010}. The data has 12007
training and 1000 testing elements (we used a random subset of the test data).
The pixel values are scaled to be in $(0,1)$.  We impose a flat prior on
$\theta$. For the proposer, we again use a random walk, this time with
covariance matrix $0.05I$ for the $784\times 784$ identity matrix $I$. The
posterior temperature is set at $T=1000$.  We run our MH test and compare with
Korattikara 2014 and Bardenet 2014; minibatch sizes and other parameters are set
to be the same value as with the Gaussian Mixtures experiment from
Section~\ref{ssec:gaussians}.

Figure~\ref{fig:logistic_performance} shows the training log likelihood and the
testing prediction accuracy, each as a function of the cumulative training data
points processed.\footnote{Note that the curves do not span the same length over
the x-axis, because our test consumes fewer samples throughout the MCMC
procedure, so the corresponding curve will ``end'' before the other two.} To
generate the curves, for each of the 5000 sampled vectors $\theta_t$,
$t\in\{1,\ldots,5000\}$, we use $\theta_t$ as the parameter for logistic
regression.  We see that our minibatch MH test is more efficient compared to the
other two methods, because it achieves similar or superior performance while
consuming fewer data points.

Figure~\ref{fig:logistic_minibatch}, in a similar manner as
Figure~\ref{fig:gauss_mix_2}, shows the histogram of minibatch sizes for all
three methods on a log-log scale. With an initial minibatch size of 100,
Korattikara 2014 and Bardenet 2014 achieve average minibatch size of 2026 and
7612 respectively over the MNIST classification task, while our method achieves
that of 163, showing significantly better performance than the benchmark test
methods.

@@

@@

We demonstrate how we can show $O(n^{-1})$ error for the quantitative CLT by
using a more precise limit distribution under an additional assumption. Let
$\mu_i$ denote the $i^{th}$ moment, and $b_i$ denote the $i^{th}$ absolute
moment of $X$. If Cramer's condition holds:
\begin{equation}\label{eq:cramers_condition}
    \lim_{t \to \infty} \sup |E(\exp(i t X))| < 1,
\end{equation}
then Equation 2.2 in Bentkus et al.'s work on Edgeworth
expansions~\citep{Bentkus97} provides the following:

\begin{lemma}\label{lem:clt_edgeworth}
Let $X_1,\ldots,X_n$ be a set of zero-mean, independent, identically-distributed
random variables with sample mean $\hat{X}$ and with $t$ defined as in Lemma 3.
If $X$ satisfies Cramer's condition, then
\begin{equation}\label{eq:clt-bounds_edgeworth}
    \sup_x\left|{\rm Pr}(t<x) - G\left(x, \frac{\mu_3}{b_2^{3/2}}\right)\right| \leq \frac{c(\epsilon,b_2,b_3,b_4,b_{4+\epsilon})}{n}
\end{equation}
where
\begin{equation}
    G_n(x,y) = \Phi(x) + \frac{y(2x^2+1)}{6\sqrt{n}}\Phi'(x).
\end{equation}
\end{lemma}
Lemma~\ref{lem:clt_edgeworth} shows that the average of the $X_i$ has a more
precise, skewed CDF limit $G_n(x,y)$ where the skew term has weight proportional
to a certain measure of skew derived from the moments:
$\frac{\mu_3}{b_2^{3/2}}$. Note that if the $X_i$ are symmetric, the weight of
the correction term is zero, and the CDF of the average of the $X_i$ converges
to $\Phi(x)$ at a rate of $O(n^{-1})$.

@@

% Daniel: don't forget this. The AISTATS website says to put it in the
% supplementary material, so I put it at the very end on a new page (to make it
% more noticeable). Obviously for the arXiv version, we don't want this there.
% Also, note to John, the reviewers for AISTATS **will have access to the
% previous NIPS reviews**, which is why I am making references to those.
\newpage
\section{NIPS 2016 Submission Statement}

>>>>

In the most similar prior works,~\citet{cutting_mh_2014} uses asymptotic
arguments based on the CLT to argue that its approximate acceptance test error
tends to zero as batch size increases, but no quantitative bounds are given.
In~\citet{icml2014c1_bardenet14}, explicit bounds are given, but they depend on
bounding:
\begin{equation}\label{eq:bad_bound}
    C_{\theta, \theta'} = \max_{1\leq i\leq N}|\log p(x_i\mid\theta') - \log p(x_i\mid\theta)|.
\end{equation}
Such bounds can be derived efficiently for models such as logistic regression,
but it is unclear how to derive them for a complex model such as a neural
network. In general, since a new $\theta'$ value is obtained each iteration, one
would need to iterate through all the $p(x_i\mid \theta')$ terms\footnote{The
sample code provided by the authors of~\citet{icml2014c1_bardenet14} in fact
computes $C_{\theta,\theta'}$ explicitly for each sample generated, i.e. it
traverses the entire data, thus providing no performance advantage over the
complete test.}. In contrast, we use quantitative forms of the Central Limit
Theorem which rely on measurable statistics from a single minibatch. Thus a
sampler using our approach does not need to see data beyond the current
minibatch.

@@

\begin{proof}
See Supplementary Material, Section~\ref{app:quant_clt}.
\end{proof}

@@

We start with a simple Gaussian mixture model, borrowing an experiment
from~\citet{langevin_2011}.  The parameter is 2-D, $\theta =
\langle \theta_1,\theta_2 \rangle$, and the parameter/data generation process is
\begin{equation}\label{eq:data_generation}
\begin{split}
    \theta &\sim \mathcal{N}(0, {\rm diag}(\sigma_1^2,\sigma_2^2)) \\
    x_i & \sim 0.5 \cdot \mathcal{N}(\theta_1, \sigma_x^2) + 0.5 \cdot \mathcal{N}(\theta_1+\theta_2, \sigma_x^2).
\end{split}
\end{equation}
We set $\sigma_1^2 = 10, \sigma_2^2 = 1$ and $\sigma_x^2=2$.  We fix $\theta =
\langle 0,1 \rangle$. The original paper sampled 100 data points from this
distribution, and estimated the posterior in the parameters. We are interested
in performance on larger problems and so sampled 1,000,000 points to form the
posterior of $p(\theta)\prod_{i=1}^{1,000,000}p(x_i\mid \theta)$ with the same
prior from Equation~(\ref{eq:data_generation}). This produces a much sharper
posterior with two very narrow peaks.  Our goal is to reproduce the original
posterior, so we adjust the temperature to $T=10,000$.  Taking logs, we get the
target as shown in the far left of Figure~\ref{fig:gauss_mix_1}.

We run MCMC with our MH test and benchmark with~\citet{cutting_mh_2014}
and~\citet{icml2014c1_bardenet14}, all with initial minibatch size $m=100$.  For
the former, we increment minibatches by 100 and for the latter, we increase it
geometrically with a ratio of $\gamma = 1.5$.  The tolerance for making a
decision in~\citet{cutting_mh_2014} is $\epsilon=0.005$, and the error bound
control parameters in~\citet{icml2014c1_bardenet14} are $p = 2$ and $\delta =
0.01$.  All methods (including ours) use the same random walk proposer with
covariance $\Sigma={\rm diag}(0.15, 0.15)$.  Since the proposer generates a
random walk, all shaping of distribution of the samples is due to the MH test.
All methods are run 5000 times to collect 5000 samples.

@@

We discretize the posterior coordinates into bins with respect to the two
components of $\theta$.  The probability $P_i$ of a sample falling into bin $i$
is the integral of the true posterior probability over the area of that bin.  A
single sample from any of the MH methods should therefore be multinomial with
distribution $P$, and a set of $n$ (ideally independent) samples should be ${\rm
Multinomial}(P,n)$.  The ideal distribution is simple, so we can use it to
measure the quality of the sample distributions rather than use general purpose
tests like KL-divergence or likelihood-ratio, which can be problematic with zero
counts in some bins as we have here.

For large $n$, the per-bin distributions are well-approximated by Poisson
distributions with parameter $\lambda_i=P_i n$. Given a set of samples
$\{\theta_1,\ldots,\theta_T\}$, let $c_j$ denote the number of individual
samples $\theta_i$ that fall in bin $j$ out of $N_{\rm bins}$ total. We have
\begin{equation}\label{eq:log_prob_poissons}
\begin{split}
    \log p(c_1, \ldots, c_{N_{\rm bins}} \mid P_1, \ldots, P_{N_{\rm bins}}) & =  \\
    \sum_{j=1}^{N_{\rm bins}} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)). & \\
\end{split}
\end{equation}
The results for each model are shown in Table~\ref{tab:poissons}.

While the Poisson results provide general guidance on the relative accuracy of
the models, it is difficult to interpret the scores. Thus, we perform
significance tests to show the difference between the MCMC-sampled distributions
and the ground-truth using the Chi-Squared distribution as the test statistic,
which we also show in Table~\ref{tab:poissons}. Both results imply that our
method is slightly superior to~\citet{cutting_mh_2014}, but slightly worse
than~\citet{icml2014c1_bardenet14}.

Figure~\ref{fig:gauss_mix_2}, however, suggests that our method dominates in
terms of speed and efficiency. It shows histograms of the (final) minibatch
sizes used each iteration by the three methods. Our method consumes
significantly less data; most minibatch sizes are smaller than 1000, and the
average size is 210.  The other methods occasionally need to consume nearly all
data points, and average minibatch sizes are 15562 and 16857. The average
minibatch sizes roughly predict the running times of these methods since all
have a running time proportional to the total data consumed, with the exception
of~\citet{icml2014c1_bardenet14}, which requires a pass over the data to compute
$C_{\theta,\theta'}$ (see Equation~(\ref{eq:bad_bound})). Using minibatch sizes
as a proxy for time also avoids discrepancies due to code optimization.

@@

\begin{figure*}[t]
	\centering
	%\includegraphics[width=0.9\linewidth]{logistic_performance.png}
	\includegraphics[width=0.85\linewidth]{logistic_regression_ll_acc_results.png}
	\caption{
    Logistic regression performance (accuracy/log likelihood) based on
    cumulative data usage.
    }
	\label{fig:logistic_performance}
\end{figure*}
\begin{figure*}[t]
	\centering
	%\includegraphics[width=0.9\linewidth]{minibatch_size_logistic.png}
	\includegraphics[width=0.85\linewidth]{logistic_regression_histograms_results.png}
	\caption{
    Counts of minibatch sizes in the MNIST logistic regression experiment
    (analogous to Figure~\ref{fig:gauss_mix_2}).
    }
	\label{fig:logistic_minibatch}
\end{figure*}

We next use logistic regression for the binary classification of 1s versus 7s on
a subset of the MNIST8M dataset, which is a larger version of
MNIST~\citep{lecun-mnisthandwrittendigit-2010} and well-suited to our desire to
run MCMC on large data. We randomly subsampled 450k training and 192k testing
points. The pixels are scaled in $[0,1]$. We impose a flat prior on $\theta$ and
again use a random walk proposer, this time with covariance matrix $0.05I$ for
the $784\times 784$ identity matrix $I$. The posterior temperature is set at
$T=1000$.  We run our MH test for 3000 samples and again compare with the two
baseline algorithms with starting minibatch size 100. To
make~\citet{cutting_mh_2014} run faster, we use a larger $\epsilon=0.05$ value.
For~\citet{icml2014c1_bardenet14}, we tuned $\gamma \in \{1.1,1.25,1.5,1.75,2\}$
before concluding that $\gamma=1.5$ was reasonable. In addition, we originally
used their suggested analytic approximation to $C_{\theta,\theta'}$, but found
that the resulting values were too high, meaning that their method needed to
consume the entire dataset each iteration. Thus, we naively compute
$C_{\theta,\theta'}$.

Figure~\ref{fig:logistic_performance} shows the testing log likelihood and
prediction accuracy, each as a function of the cumulative training data points
processed.\footnote{Note that the curves do not span the same length over the
x-axis, because our test consumes fewer samples throughout the MCMC procedure,
so the corresponding curve will ``end'' before the other two.} To generate the
curves, for each of the 3000 sampled vectors $\theta_t$,
$t\in\{1,\ldots,3000\}$, we use $\theta_t$ as the parameter for logistic
regression.  Our minibatch MH test is more efficient in terms of
accuracy, achieving convergence using roughly half as many elements
compared to~\citet{cutting_mh_2014} and \textbf{TODO TODO TODO} compared
to~\citet{icml2014c1_bardenet14}, though its log likelihood results lag slightly
behind the former algorithm during the very early stages.

Figure~\ref{fig:logistic_minibatch}, in a similar manner as
Figure~\ref{fig:gauss_mix_2}, shows the histogram of minibatch sizes for all
three methods on a log-log scale. With an initial size of 100, our method
achieves an average minibatch size of 393, far smaller than the averages of the
other two methods, which is due to their longer-tailed distributions.

@@

\section{Proof of Lemma~\ref{lem:quant_clt}}\label{app:quant_clt}

The following bound is given immediately after Corollary 2 from~\citet{explicit-clt05}:
\begin{align*}
-6.4E|X|^3-2E|X| &\leq \sup_x|{\rm Pr}(t<x)-\Phi(x)|{\sqrt{n}} \\
&\leq 1.36E|X|^3.
\end{align*}
This bound applies to $x\geq 0$. Applying the bound to $-x$ when $x<0$
and combining with $x>0$, we obtain the weaker but unqualified bound
in Equation~(\ref{eq:clt-bounds}).

@@

We demonstrate how we can show $O(n^{-1})$ error for the quantitative CLT by
using a more precise limit distribution under an additional assumption. Let
$\mu_i$ denote the $i^{th}$ moment, and $b_i$ denote the $i^{th}$ absolute
moment of $X$. If Cramer's condition holds:
\begin{equation}\label{eq:cramers_condition}
    \lim_{t \to \infty} \sup |E(\exp(i t X))| < 1,
\end{equation}
then Equation 2.2 in Bentkus et al.'s work on Edgeworth
expansions~\citep{Bentkus97} provides:

\begin{lemma}\label{lem:clt_edgeworth}
Let $X_1,\ldots,X_n$ be a set of zero-mean, independent, identically-distributed
random variables with sample mean $\hat{X}$ and with $t$ defined as in Lemma 3.
If $X$ satisfies Cramer's condition, then
%\begin{equation}\label{eq:clt-bounds_edgeworth}
\[
    \sup_x\left|{\rm Pr}(t<x) - G\left(x, \frac{\mu_3}{b_2^{3/2}}\right)\right| \leq \frac{c(\epsilon,b_2,b_3,b_4,b_{4+\epsilon})}{n}
\]
%\end{equation}
where
\begin{equation}
    G_n(x,y) = \Phi(x) + \frac{y(2x^2+1)}{6\sqrt{n}}\Phi'(x).
\end{equation}
\end{lemma}
Lemma~\ref{lem:clt_edgeworth} shows that the average of the $X_i$ has a more
precise, skewed CDF limit $G_n(x,y)$ where the skew term has weight proportional
to a certain measure of skew derived from the moments:
$\mu_3/b_2^{3/2}$. Note that if the $X_i$ are symmetric, the weight of
the correction term is zero, and the CDF of the average of the $X_i$ converges
to $\Phi(x)$ at a rate of $O(n^{-1})$.

@@

% Daniel: don't forget this. The AISTATS website says to put it in the
% supplementary material, so I put it at the very end on a new page (to make it
% more noticeable). Obviously for the arXiv version, we don't want this there.
% Also, note to John, the reviewers for AISTATS **will have access to the
% previous NIPS reviews**, which is why I am making references to those.
\clearpage
\section{NIPS 2016 Submission Statement}
